Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
fixed soem todos

\paragraph{\our for continual learning}
% Definition of CL -> a sequence of tasks 
In the continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{N_t}$, which after the task is discarded and cannot be accessed in the following stages of the training. Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting. In the same way, after each task, we can use \our method to build a compact representation of the neural network and then exploit this representation to construct a functional regularizer to add to the training loss for the subsequent tasks. Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art \todo{Could add a noun after state-of-the-art} on CL benchmarks. However, they are limited to using subset approximations of the posterior. Instead, we use the sparse data term posterior, see \cref{app:cl} for details.
%, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
\our is a more principled approach since the resultant GP is a low-rank approximation of the full data which ensures information is not lost. %, essentially what the sparse dual variables do.   \todo{this term is replacing the missing data}
% Where the regularizer comes from

@@

In \cref{tbl:uci} (right) we compare to the subset GP method from \cite{immer2021improving} whilst using only $M=32$ inducing points.
It shows that \our is able to summarize the full data set more effectively than the GP subset method as it maintains predictive performance
whilst using fewer inducing points.
\cref{fig:uci} further shows that as the number of inducing points is lowered $M=512,\ldots, 16$, \our is able to maintain a much better NLPD than the GP subset.
These results demonstrate \our's sparse representation captures information from the entire data set and as a result provides good uncertainty estimates.
We provide full details of our experiments and further results using $M=16,32,64,128,256$ in \cref{app:uci}.
% benefits of \our in summarizing the full data distribution onto a small set of inducing
% points over just picking a random subset.

@@

	% Import table content
	\input{tables/cl_table_1}
\end{wraptable}
%
% Overview
We aim to highlight our sparse representation's ability to retain previous knowledge for continual learning (CL) (as in \cref{sec:sequential}). We consider the single-head (SH) setting that is harder and more realistic than multi-head (MH)~\citep{van2019three}.	 \todo{can't find the bibtex for their NIPS workshop paper} % typically hard and more competitive \cite{}
%
% Benchmarks/architectures
 Our \our-based regularizer is evaluated on three CL benchmarks, specifically Split-MNIST (S-MNIST), Split-FashionMNIST (S-FMNIST), and the 10-tasks Permuted-MNIST (P-MNIST). We adhere to the same setups as outlined in \cite{rudner2022continual, pan2020continual}, which involve utilizing a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST, to ensure consistency. Please refer to \cref{app:cl-exp} for full details.

>>>>

\paragraph{\our for continual learning}
% Definition of CL -> a sequence of tasks 
In the continual learning setting, the training is divided into $T$ tasks, each with its training data set $\dataset_t = \{(\mathbf{x}_{i}, \mathbf{y}_{i})\}_{i=1}^{N_t}$, which after the task is discarded and cannot be accessed in the following stages of the training. Rehearsal and function regularization-based models keep a subset of the training data for each task to help the model alleviate forgetting. In the same way, after each task, we can use \our method to build a compact representation of the neural network and then exploit this representation to construct a functional regularizer to add to the training loss for the subsequent tasks. Recently proposed GP-based regularizers \cite{ pan2020continual, rudner2022continual} have shown better performances than weight space equivalents getting state-of-the-art results \todo{Could add a noun after state-of-the-art} on CL benchmarks. However, they are limited to using subset approximations of the posterior. Instead, we use the sparse data term posterior, see \cref{app:cl} for details.
%, which in practice means randomly selecting some data computing its posterior at only those points and then using that as the regularizer. 
\our is a more principled approach since the resultant GP is a low-rank approximation of the full data which ensures information is not lost. %, essentially what the sparse dual variables do.   \todo{this term is replacing the missing data}
% Where the regularizer comes from

@@

In \cref{tbl:uci} (right) we compare to the subset GP method from \cite{immer2021improving} whilst using only $M=32$ inducing points.
It shows that \our is able to summarize the full data set more effectively than the GP subset method as it maintains predictive performance
whilst using fewer inducing points.
\cref{fig:uci} further shows that as the number of inducing points is lowered $M=512 \rightarrow 16$, \our is able to maintain a much better NLPD than the GP subset.
These results demonstrate \our's sparse representation captures information from the entire data set and as a result provides good uncertainty estimates.
We provide full details of our experiments and further results using $M=16,32,64,128,256$ in \cref{app:uci}.
% benefits of \our in summarizing the full data distribution onto a small set of inducing
% points over just picking a random subset.

@@

	% Import table content
	\input{tables/cl_table_1}
\end{wraptable}
%
% Overview
We aim to highlight our sparse representation's ability to retain previous knowledge for continual learning (CL) (as in \cref{sec:sequential}). We consider the single-head (SH) setting that is harder and more realistic than multi-head (MH)~\citep{van2019three}.
% Benchmarks/architectures
 Our \our-based regularizer is evaluated on three CL benchmarks, specifically Split-MNIST (S-MNIST), Split-FashionMNIST (S-FMNIST), and the 10-tasks Permuted-MNIST (P-MNIST). We adhere to the same setups as outlined in \cite{rudner2022continual, pan2020continual}, which involve utilizing a two-layer MLP with 256 hidden units and ReLU activation for S-MNIST and S-FMNIST, and a two-layer MLP with 100 hidden units for P-MNIST, to ensure consistency. Please refer to \cref{app:cl-exp} for full details.
